---
title: "Prediction Assignment"
author: "ZZ"
date: "12/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### 1.Exucutive Summary 
 
The goal for this analysis is quantify how well people perform on their using the data from accelerometers on the belt, forearm, arm, and dumbbell of 6 participants.

Given data of 6 participants activities from the accelerometers. 
Use the training set and other variables to predict with.
To predict the manner in which they performed in the exercise.


### Prep work



```{r }
#install.packages("caret")
#install.packages("RCurl")
#install.packages("corrplot")
#install.packages("data.table")
#install.packages("dplyr")

library("data.table")
library("dplyr")
library("caret")
library("RCurl")
library("corrplot")

setwd("C:\\Users\\zengzeng.yang\\Documents\\R")


testdata <- read.csv("pml-testing.csv", header = TRUE)
trainingdata <- read.csv("pml-training.csv", header = TRUE)

str(trainingdata)
str(testdata)

```

```{r}

dim(testdata)
dim(trainingdata)

```


160 variables for both training and data set.
We need to remove the near zero variance variable or columns that contain N/A missing values

###partition of training data set and cleaning data

```{r}


#training <- trainingdata[,colSums(is.na(trainingdata))== 0]

set.seed(32343)
inTrain <- createDataPartition(trainingdata$classe, p =.7,list = FALSE)
traindata <- trainingdata[inTrain,]
testdata <- trainingdata[-inTrain,]
dim(traindata)
dim(testdata)

# remove NA value and near zero variance variables
NZV <- nearZeroVar(traindata)
traindata <- trainingdata[,-NZV]
testdata <- testdata[,-NZV]
dim(traindata)
dim(testdata)

?sapply
NAtrain <- sapply(traindata, function(x)mean(is.na(x)))>.9
NAtest <- sapply(testdata, function(x)mean(is.na(x)))>.9

traindata <- traindata[, NAtrain == F]
testdata <- testdata[, NAtest == F]


dim(traindata)
dim(testdata)


traindata <- traindata[, -(1:5)]
testdata <- traindata[, -(1:5)]


traindata

dim(traindata)
dim(testdata)

```

```{ r results = 'hide', message = FALSE }
correlation <- cor(testdata,-49)
corrplot(correlation, method = "circle")

## Classification Tree Method

trcontrol <- trainControl(method = "cv", number = 5)
model_CT <- train(classe~., method = "rpart", data = traindata, trControl = trcontrol)

fancyRpartPlot(model_CT$finalModel)

##install.packages("e1071")
##install.packages("rattle")
library(rattle)

fancyRpartPlot(model_CT$finalModel)

predict_train <- predict(model_CT, newdata = testdata)

ClassTree <- confusionMatrix(testdata$classe,predict_train)


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
